---
title: "cohealth Kensington GP Clinic — Patient Feedback Survey 2026"
subtitle: "P3CEQ person-centred care results and patient experience summary"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
    theme: flatly
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(readxl)
library(scales)
library(knitr)

csv_path  <- "Patient feedback questionnaire — cohealth Kensington GP clinic 2026_WIDE.csv"
form_path <- "kensington_p3ceq_2026_surveycto.xlsx"

# ---- palette (dataviz skill default palette) ---------------------------
pal_blue   <- "#2a78d6"
pal_seq    <- c("#9ec5f4", "#6da7ec", "#3987e5", "#2a78d6", "#1c5cab") # light -> dark, 5 steps
pal_cat    <- c("#2a78d6", "#eb6834", "#1baf7a", "#eda100",
                 "#e87ba4", "#008300", "#4a3aa7", "#e34948")
ink_primary   <- "#0b0b0b"
ink_secondary <- "#52514e"
ink_muted     <- "#898781"
grid_col      <- "#e1e0d9"
baseline_col  <- "#c3c2b7"

theme_report <- theme_minimal(base_size = 12) +
  theme(
    text = element_text(colour = ink_primary),
    plot.title = element_text(face = "bold", size = 13, colour = ink_primary),
    plot.subtitle = element_text(colour = ink_secondary, size = 10.5),
    axis.text = element_text(colour = ink_secondary),
    axis.title = element_text(colour = ink_secondary, size = 10),
    panel.grid.major.x = element_line(colour = grid_col, linewidth = 0.3),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.y = element_line(colour = baseline_col, linewidth = 0.4),
    axis.ticks = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    legend.justification = "left",
    plot.title.position = "plot"
  )
theme_set(theme_report)

strip_html <- function(x) x |> str_remove_all("<[^>]+>") |> str_squish()
```

## About this report

This report summarises responses to the 2026 cohealth Kensington GP clinic patient feedback
survey. The survey combines three blocks: clinic-specific items about reception, privacy and
care coordination; the validated **P3CEQ** (Person Centred Coordinated Care Experiences
Questionnaire); and a set of demographic questions. Full item wording and response options are
defined in `r form_path`; the P3CEQ instrument and its official scoring rules are documented in
`P3C-PEQ with scoring.pdf`.

```{r}
#| label: load-data

raw <- read_csv(csv_path, show_col_types = FALSE, name_repair = "minimal")

form_survey  <- read_excel(form_path, sheet = "survey")  |> select(type, name, label)
form_choices <- read_excel(form_path, sheet = "choices") |> mutate(value = as.character(value))

choice_labels <- function(list_name) {
  form_choices |>
    filter(list_name == !!list_name) |>
    select(value, label) |>
    deframe()
}

item_label <- function(varname) {
  lab <- form_survey$label[form_survey$name == varname]
  if (length(lab) == 0 || is.na(lab)) return(varname)
  strip_html(lab)
}

survey <- raw |> filter(consent == 1)
```

### Participation

```{r}
#| label: participation

n_total     <- nrow(raw)
n_consented <- nrow(survey)
n_declined  <- n_total - n_consented

dates <- raw |>
  mutate(submit_dt = lubridate::mdy_hms(SubmissionDate)) |>
  summarise(first = min(submit_dt, na.rm = TRUE), last = max(submit_dt, na.rm = TRUE))

med_duration <- median(survey$duration, na.rm = TRUE) / 60

tibble(
  Measure = c("Total submissions", "Consented (analysed below)", "Declined consent",
              "Collection period", "Median completion time"),
  Value = c(
    n_total,
    n_consented,
    n_declined,
    paste(format(dates$first, "%d %b %Y"), "–", format(dates$last, "%d %b %Y")),
    paste0(round(med_duration, 1), " minutes")
  )
) |>
  kable(align = "l")
```

Of `r n_total` submissions, `r n_consented` respondents consented to take part; the summaries
below are based on those `r n_consented` responses. `r n_declined` people opened the survey and
declined.

## P3CEQ: person-centred coordinated care experience

Questions 4–20 of the survey reproduce the P3CEQ instrument, adapted into cohealth Kensington's
own response wording. Raw response codes are recoded onto the official P3CEQ 0–3 scale before
scoring, following the mapping in `CLAUDE.md`. The total score sums the ten P3CEQ items
(Q7 contributes the average of its four sub-items 7a–7d), giving a score out of 30 where higher
means a more person-centred, coordinated care experience. Two optional subscales are also
reported: **person-centred (PC)** and **care coordination (CC)**.

```{r}
#| label: p3ceq-recode

recode_yesdef  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q10     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 3, x == 4 ~ 0, TRUE ~ NA_real_)
recode_yesno3  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 0, TRUE ~ NA_real_)
recode_extent5 <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q17     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 1, x == 4 ~ 2, x == 5 ~ 3, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q18     <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 2, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q19     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)

p3ceq <- survey |>
  transmute(
    KEY,
    p1  = recode_yesdef(q4),
    p2  = recode_yesdef(q5),
    p3  = recode_yesdef(q6),
    p4  = recode_yesdef(q7),
    p5  = recode_yesdef(q8),
    p6  = recode_q10(q10),
    p7a = recode_yesno3(q13),
    p7b = recode_yesno3(q14),
    p7c = recode_extent5(q15),
    p7d = recode_extent5(q16),
    p8  = recode_q17(q17),
    p9  = recode_q18(q18),
    p10 = recode_q19(q19)
  ) |>
  mutate(
    p7 = if_else(p7a == 0, 0, rowMeans(cbind(p7a, p7b, p7c, p7d), na.rm = FALSE))
  ) |>
  mutate(
    total       = p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10,
    pc_subscale = p1 + p2 + p3 + p4 + p5 + p8 + p9 + p10,
    cc_subscale = p5 + p6 + p7 + p8 + p9
  )
```

### Total and subscale scores

```{r}
#| label: p3ceq-scores

score_summary <- function(x, label, max_score) {
  tibble(
    Score = label,
    n = sum(!is.na(x)),
    Mean = mean(x, na.rm = TRUE),
    Median = median(x, na.rm = TRUE),
    SD = sd(x, na.rm = TRUE),
    `Out of` = max_score
  )
}

bind_rows(
  score_summary(p3ceq$total, "P3CEQ total", 30),
  score_summary(p3ceq$pc_subscale, "Person-centred subscale (PC)", 24),
  score_summary(p3ceq$cc_subscale, "Care coordination subscale (CC)", 15)
) |>
  mutate(across(c(Mean, Median, SD), \(x) round(x, 1))) |>
  kable(align = "lrrrrr")
```

```{r}
#| label: fig-p3ceq-total-dist
#| fig-cap: "Distribution of P3CEQ total scores (0–30, higher = more person-centred)"

p3ceq |>
  filter(!is.na(total)) |>
  ggplot(aes(total)) +
  geom_histogram(binwidth = 2, boundary = 0, fill = pal_blue, colour = "white", linewidth = 0.3) +
  scale_x_continuous(limits = c(0, 30), breaks = seq(0, 30, 5)) +
  labs(x = "P3CEQ total score", y = "Respondents", title = "P3CEQ total score distribution")
```

### Item-level results

```{r}
#| label: fig-p3ceq-items
#| fig-cap: "Mean score per P3CEQ item (0–3 scale, higher = better)"
#| fig-height: 5

p3ceq_item_labels <- c(
  p1  = "Q1. Discussed what matters to you",
  p2  = "Q2. Involved in decisions about your care",
  p3  = "Q3. Considered as a whole person",
  p4  = "Q4. Didn't have to repeat information*",
  p5  = "Q5. Healthcare joined up / works for you",
  p6  = "Q6. Has a single coordinating professional",
  p7  = "Q7. Care plan in place and followed (avg of 7a–7d)",
  p8  = "Q8. Enough support to manage own health",
  p9  = "Q9. Useful information when needed",
  p10 = "Q10. Confident managing own health"
)

p3ceq |>
  select(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10) |>
  pivot_longer(everything(), names_to = "item", values_to = "score") |>
  filter(!is.na(score)) |>
  group_by(item) |>
  summarise(mean_score = mean(score), n = n(), .groups = "drop") |>
  mutate(item = fct_reorder(p3ceq_item_labels[item], mean_score)) |>
  ggplot(aes(mean_score, item)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = number(mean_score, accuracy = 0.1)),
            hjust = -0.3, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, 3.4), breaks = 0:3) +
  labs(x = "Mean score (0–3)", y = NULL,
       title = "P3CEQ item scores",
       subtitle = "*Q4 is reverse-scored: a high score means information rarely had to be repeated")
```

## Clinic-specific experience

Questions 1–3 ask about reception staff, privacy, and how well your clinician coordinated with
other health professionals, each rated on a 5-point Poor–Excellent scale (with "N/A" and "Don't
know" excluded from the summaries below).

```{r}
#| label: fig-rate7-items
#| fig-cap: "Reception, privacy and clinician coordination — response distribution (valid responses only)"
#| fig-width: 9
#| fig-height: 5.5

rate7_labs <- choice_labels("rate7")
rate7_valid <- names(rate7_labs)[!rate7_labs %in% c("N/A", "Don't know")]

rate7_vars <- c("q1a", "q1b", "q1c", "q2a", "q2b", "q2c", "q3a", "q3b", "q3c", "q3d")

rate7_long <- survey |>
  select(all_of(rate7_vars)) |>
  mutate(across(everything(), as.character)) |>
  pivot_longer(everything(), names_to = "var", values_to = "value") |>
  filter(value %in% rate7_valid) |>
  mutate(
    item = fct_rev(fct_inorder(map_chr(var, item_label))),
    response = factor(rate7_labs[value], levels = rate7_labs[rate7_valid])
  )

rate7_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(pct, item, fill = response)) +
  geom_col(width = 0.7, position = position_stack(reverse = TRUE)) +
  scale_fill_manual(values = pal_seq) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
  labs(x = "Share of valid responses", y = NULL, title = "Ratings by item") +
  theme(legend.position = "top")
```

```{r}
#| label: rate7-comments

comment_table <- function(var, heading) {
  txt <- survey[[var]][!is.na(survey[[var]]) & str_trim(survey[[var]]) != ""]
  if (length(txt) == 0) return(invisible(NULL))
  cat("\n**", heading, "** (", length(txt), " comments)\n\n", sep = "")
  cat(paste0("- ", txt, collapse = "\n"), "\n")
}
```

::: {.callout-note collapse="true"}
## Free-text comments on reception, privacy and coordination

```{r}
#| label: rate7-comments-out
#| results: asis

comment_table("q1_comment", "Reception staff")
comment_table("q2_comment", "Privacy")
comment_table("q3_comment", "Coordination with other healthcare professionals")
```
:::

## Long-term conditions

```{r}
#| label: fig-conditions
#| fig-cap: "Long-term conditions reported by respondents"
#| fig-width: 8
#| fig-height: 7

summarise_multiselect <- function(data, prefix, list_name) {
  labs <- choice_labels(list_name)
  cols <- data |> select(matches(paste0("^", prefix, "_[0-9]+$")))
  tibble(
    value = str_remove(names(cols), paste0("^", prefix, "_")),
    n = colSums(cols, na.rm = TRUE)
  ) |>
    mutate(label = labs[value], pct = n / nrow(data)) |>
    arrange(desc(n))
}

conditions <- summarise_multiselect(survey, "q9", "conditions")

conditions |>
  mutate(label = fct_reorder(str_wrap(label, 28), n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(conditions$n) * 1.15)) +
  labs(x = "Respondents", y = NULL, title = "Long-term conditions (Q9)",
       subtitle = paste0("Out of ", n_consented, " respondents; multiple selections allowed"))
```

## Respondent profile

```{r}
#| label: fig-demographics
#| fig-cap: "Respondent demographics"
#| fig-width: 11
#| fig-height: 9

demo_vars <- tribble(
  ~var, ~list, ~title,
  "q22", "q22opts", "Gender (Q22)",
  "q26", "q26opts", "Age (Q26)",
  "q27", "q27opts", "Time at this practice (Q27)",
  "q29", "q29opts", "Visits in past 12 months (Q29)",
  "q30", "q30opts", "Highest education level (Q30)",
  "q31", "q31opts", "Visit was for self or someone else (Q31)"
)

demo_long <- pmap_dfr(demo_vars, function(var, list, title) {
  labs <- choice_labels(list)
  survey |>
    mutate(value = as.character(.data[[var]])) |>
    filter(!is.na(value), value %in% names(labs)) |>
    count(value) |>
    mutate(
      question = title,
      response = factor(labs[value], levels = labs),
      pct = n / sum(n)
    )
})

demo_long |>
  ggplot(aes(pct, fct_rev(response))) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 1)), hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.25))) +
  facet_wrap(~question, scales = "free_y", ncol = 2) +
  labs(x = NULL, y = NULL, title = "Who responded") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

```{r}
#| label: demographics-extra

atsi_pct    <- mean(survey$q23 == 1, na.rm = TRUE)
other_gp_pct <- mean(survey$q24 == 1, na.rm = TRUE)

languages <- summarise_multiselect(survey, "q25", "languages")
concession <- summarise_multiselect(survey, "q28", "q28opts")

tibble(
  Measure = c(
    "Identify as Aboriginal and/or Torres Strait Islander (Q23)",
    "Attended another general practice in the last year (Q24)"
  ),
  Value = percent(c(atsi_pct, other_gp_pct), accuracy = 1)
) |>
  kable(align = "l")
```

```{r}
#| label: fig-languages
#| fig-cap: "Languages spoken at home (Q25) and concession cards held (Q28)"
#| fig-width: 10
#| fig-height: 4.5

bind_rows(
  languages |> mutate(facet = "Languages spoken at home (Q25)"),
  concession |> mutate(facet = "Concession cards held (Q28)")
) |>
  mutate(label = fct_reorder(label, n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.2, colour = ink_secondary) +
  facet_wrap(~facet, scales = "free", ncol = 2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Respondents", y = NULL) +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

A large share of the Q25 "Other" responses come from a wide mix of languages, none individually
common enough to be listed as its own choice on the form. `q25_other` holds what respondents
typed in; below are those free-text responses as given (grouped only where the text matches
exactly), most-common first.

```{r}
#| label: fig-languages-other
#| fig-cap: "Q25 'Other' responses: languages named in free text"
#| fig-width: 7
#| fig-height: 4

other_langs <- survey |>
  mutate(q25_other = str_squish(q25_other)) |>
  filter(!is.na(q25_other), q25_other != "") |>
  count(q25_other, sort = TRUE)

other_langs |>
  mutate(q25_other = fct_reorder(q25_other, n)) |>
  ggplot(aes(n, q25_other)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(other_langs$n) * 1.15), breaks = scales::breaks_pretty()) +
  labs(x = "Respondents", y = NULL, title = "Q25 \"Other\": languages named in free text",
       subtitle = paste0(sum(other_langs$n), " free-text responses, out of ",
                          languages$n[languages$label == "Other"], " respondents who selected \"Other\""))
```

## What patients said

Question 21 asked what one thing respondents would change about the practice.

::: {.callout-note collapse="true"}
## Free-text: "If you could change one thing about the practice..." (Q21)

```{r}
#| label: q21-comments
#| results: asis

comment_table("q21", "Suggested changes")
```
:::
