---
title: "cohealth Kensington GP Clinic — Patient Feedback Survey 2026"
subtitle: "P3CEQ person-centred care results and patient experience summary"
number-sections: true
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
    theme: flatly
  pdf:
    toc: true
    toc-depth: 3
    number-sections: false
    fig-pos: "H"
    geometry:
      - margin=2.5cm
    echo: false
execute:
  warning: false
  message: false
references:
  - type: webpage
    id: paris
    author:
      - literal: "Australian Commission on Safety and Quality in Health Care"
    title: "PaRIS Survey - Australian National Report 2025"
    url: "https://www.safetyandquality.gov.au/resources/paris-survey-australian-national-report-2025"
    issued:
      date-parts:
        - [2025]
    accessed:
      date-parts:
        - [2026, 9, 12]
  - type: webpage
    id: racgppatientfeedbackguide
    author:
      - literal: "RACGP"
    title: "Standards for general practices (5th edition), Patient feedback guide"
    url: "https://www.racgp.org.au/running-a-practice/practice-standards/standards-5th-edition/patient-feedback-guide"
    issued:
      date-parts:
        - [2023, 8]
    accessed:
      date-parts:
        - [2026, 9, 12]
  - type: webpage
    id: p3c_p3c-eq
    author:
      - literal: "University of Plymouth"
    title: "Person centred coordinated experience questionnaire P3C-EQ"
    url: "http://p3c.org.uk/prom-detail/29#ChildVerticalTab_11"
    issued:
      date-parts:
        - [2017]
    accessed:
      date-parts:
        - [2026, 9, 12]
  - type: report
    id: oecd-paris
    author:
      - family: "OECD"
    publisher: "OECD Publishing"
    location: "Paris"
    title: "Does Healthcare Deliver?: Results from the Patient-Reported Indicator Surveys (PaRIS)"
    shorttitle:
      - literal: "Does Healthcare Deliver?: Results from the Patient-Reported Indicator Surveys (PaRIS)"
    url: "https://doi.org/10.1787/c8af05a5-en"
    DOI: "10.1787/c8af05a5-en"
    issued:
      year: 2025
  - type: article-journal
    id: groenewegen2024
    author:
      - family: "Groenewegen"
        given: "Peter"
      - family: "Spreeuwenberg"
        given: "Peter"
      - family: "Timans"
        given: "Rob"
      - family: "Groene"
        given: "Oliver"
      - family: "Suñol"
        given: "Rosa"
      - family: "Valderas"
        given: "Jose Maria"
      - family: "Rijken"
        given: "Mieke"
    title: "Data analysis plan of the OECD PaRIS survey: leveraging a multi-level approach to analyse data collected from people living with chronic conditions and their primary care practices in 20 countries"
    container-title: "BMC Research Notes"
    volume: 17
    page: "157"
    url: "https://doi.org/10.1186/s13104-024-06815-7"
    DOI: "10.1186/s13104-024-06815-7"
    issued:
      date-parts:
        - [2024]
editor: source
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(readxl)
library(scales)
library(knitr)

# Figures are sized (fig-width/fig-height) per chunk for comfortable HTML
# layout; out.width scales the embedded image to fit the page/column in both
# HTML and PDF output so nothing overflows a PDF page's margins. cairo_pdf
# (instead of the base "pdf" device) renders Unicode characters (en dashes,
# em dashes) correctly when the format is PDF.
opts_chunk$set(out.width = "100%")
if (knitr::is_latex_output()) opts_chunk$set(dev = "cairo_pdf")

csv_path  <- "Patient feedback questionnaire — cohealth Kensington GP clinic 2026_WIDE.csv"
form_path <- "kensington_p3ceq_2026_surveycto.xlsx"

# ---- palette (dataviz skill default palette) ---------------------------
pal_blue   <- "#2a78d6"
pal_seq    <- c("#9ec5f4", "#6da7ec", "#3987e5", "#2a78d6", "#1c5cab") # light -> dark, 5 steps
pal_cat    <- c("#2a78d6", "#eb6834", "#1baf7a", "#eda100",
                 "#e87ba4", "#008300", "#4a3aa7", "#e34948")
ink_primary   <- "#0b0b0b"
ink_secondary <- "#52514e"
ink_muted     <- "#898781"
grid_col      <- "#e1e0d9"
baseline_col  <- "#c3c2b7"

theme_report <- theme_minimal(base_size = 12) +
  theme(
    text = element_text(colour = ink_primary),
    plot.title = element_text(face = "bold", size = 13, colour = ink_primary),
    plot.subtitle = element_text(colour = ink_secondary, size = 10.5),
    axis.text = element_text(colour = ink_secondary),
    axis.title = element_text(colour = ink_secondary, size = 10),
    panel.grid.major.x = element_line(colour = grid_col, linewidth = 0.3),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.y = element_line(colour = baseline_col, linewidth = 0.4),
    axis.ticks = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    legend.justification = "left",
    plot.title.position = "plot"
  )
theme_set(theme_report)

strip_html <- function(x) x |> str_remove_all("<[^>]+>") |> str_squish()
```

## About this report

This report summarises responses to the 2026 cohealth Kensington GP clinic patient feedback
survey. The survey combines clinic-specific items about reception, privacy,
continuity of care (with a focus on care coordination) and demographic questions
from "Standards for general practices (5th edition), Patient feedback guide" [@racgppatientfeedbackguide]
and the validated **P3CEQ** (Person Centred Coordinated Care Experiences Questionnaire) [@p3c_p3c-eq].

Full item wording and response options are
defined in `` `r form_path` ``; the P3CEQ instrument and its scoring rules are documented in
`P3C-PEQ with scoring.pdf`.

```{r}
#| label: load-data

raw <- read_csv(csv_path, show_col_types = FALSE, name_repair = "minimal")

# Entries copied in from a paper survey are marked in q1_comment with "PAPER" optionally
# followed by a number (e.g. "PAPER1", "PAPER 12"). Flag those rows, then strip the marker
# out of q1_comment so it doesn't show up as if it were part of the patient's comment.
paper_marker <- regex("PAPER\\s*\\d*")
raw <- raw |>
  mutate(
    # coalesce so a blank q1_comment (str_detect would return NA) reads as "not paper", not NA
    is_paper = coalesce(str_detect(q1_comment, paper_marker), FALSE),
    q1_comment = str_remove(q1_comment, paper_marker) |> str_squish() |> na_if("")
  )

form_survey  <- read_excel(form_path, sheet = "survey")  |> select(type, name, label)
form_choices <- read_excel(form_path, sheet = "choices") |> mutate(value = as.character(value))

# return a labelled vector of choice responses
choice_labels <- function(list_name) {
  form_choices |>
    filter(list_name == !!list_name) |>
    select(value, label) |>
    deframe() # change dataframe to vector
}

# return 'labels' of a question (often the question itself)
item_label <- function(varname) {
  lab <- form_survey$label[form_survey$name == varname]
  if (length(lab) == 0 || is.na(lab)) return(varname)
  strip_html(lab)
}

survey <- raw |> filter(consent == 1)
```

### Participation

```{r}
#| label: participation

n_total     <- nrow(raw)
n_consented <- nrow(survey)
n_declined  <- n_total - n_consented

n_paper  <- sum(survey$is_paper)
n_online <- n_consented - n_paper

# Collection period and completion time are only meaningful for the online arm: a paper
# form's SubmissionDate/duration record when staff later transcribed it, not when the
# patient actually filled it in (paper collection dates are given in the prose below instead).
dates <- raw |>
  filter(!is_paper) |>
  mutate(submit_dt = lubridate::mdy_hms(SubmissionDate)) |>
  summarise(first = min(submit_dt, na.rm = TRUE), last = max(submit_dt, na.rm = TRUE))

med_duration <- median(survey$duration[!survey$is_paper], na.rm = TRUE) / 60

tibble(
  Measure = c("Total submissions", "Consented (analysed below)", "— Online", "— Paper",
              "Declined consent (online)", "Collection period (online)",
              "Median completion time (online)"),
  Value = c(
    n_total,
    n_consented,
    n_online,
    n_paper,
    n_declined,
    paste(format(dates$first, "%d %b %Y"), "–", format(dates$last, "%d %b %Y")),
    paste0(round(med_duration, 1), " minutes")
  )
) |>
  kable(align = "l")
```

Both paper and online versions of the survey were made available. The paper and online versions of the survey were
identical and available in English only.

Paper versions of the survey were offered to patients in the waiting and consulting rooms (11th August to 11th September 2026).

RACGP active patients (three visits or more in the past two years with GP clinicians
at the cohealth Kensington site) who also had seen a cohealth Kensington GP at least once in 2026 and aged 20 years or above
were sent a SMS invitation to complete the survey online on 5th September 2026. 948 patients were invited to complete the survey
through an SMS invitation.

The summaries below are based on those `r n_consented` responses. `r n_declined` people opened the survey online and
declined.

## P3CEQ: person-centred coordinated care experience

Questions 4–20 of the survey reproduce the P3CEQ instrument, using wording as adapted by
the PaRIS international patient reported indicator survey [ACSQHC, -@paris]. Raw response codes are recoded onto the official P3CEQ 0–3 scale before
scoring, following the mapping in `CLAUDE.md`. The total score sums the ten P3CEQ items
(Q7 contributes the average of its four sub-items 7a–7d), giving a score out of 30 where higher
means a more person-centred, coordinated care experience. Two optional subscales are also
reported: **person-centred (PC)** and **care coordination (CC)**.

```{r}
#| label: p3ceq-recode

recode_yesdef  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)
# q7 ("Were there times when you had to repeat information...") is a negatively-framed yesdef
# item, unlike q4/q5/q6/q8: "Yes, definitely" here means the bad thing happened a lot, not that
# a good thing happened. The original P3CEQ Q4 is reverse-scored for exactly this reason (Not at
# all=3 ... Always=0), so the recode must flip polarity vs. recode_yesdef to keep "higher = better"
# consistent across all ten items.
recode_yesdef_reverse <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q10     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 3, x == 4 ~ 0, TRUE ~ NA_real_)
recode_yesno3  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 0, TRUE ~ NA_real_)
recode_extent5 <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q17     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 1, x == 4 ~ 2, x == 5 ~ 3, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q18     <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 2, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q19     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)

p3ceq <- survey |>
  mutate(
    KEY,
    p1  = recode_yesdef(q4),
    p2  = recode_yesdef(q5),
    p3  = recode_yesdef(q6),
    p4  = recode_yesdef_reverse(q7),
    p5  = recode_yesdef(q8),
    p6  = recode_q10(q10),
    p7a = recode_yesno3(q13),
    p7b = recode_yesno3(q14),
    p7c = recode_extent5(q15),
    p7d = recode_extent5(q16),
    p8  = recode_q17(q17),
    p9  = recode_q18(q18),
    p10 = recode_q19(q19),
    .keep = "none"
  ) |>
  mutate(
    p7 = if_else(p7a == 0, 0, rowMeans(cbind(p7a, p7b, p7c, p7d), na.rm = FALSE))
  ) |>
  mutate(
    total       = p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10,
    pc_subscale = p1 + p2 + p3 + p4 + p5 + p8 + p9 + p10,
    cc_subscale = p5 + p6 + p7 + p8 + p9
  )
```

### Total and subscale scores

```{r}
#| label: p3ceq-scores

score_summary <- function(x, label, max_score) {
  tibble(
    Score = label,
    n = sum(!is.na(x)),
    Mean = mean(x, na.rm = TRUE),
    Median = median(x, na.rm = TRUE),
    SD = sd(x, na.rm = TRUE),
    `Out of` = max_score
  )
}

bind_rows(
  score_summary(p3ceq$total, "P3CEQ total", 30),
  score_summary(p3ceq$pc_subscale, "Person-centred subscale (PC)", 24),
  score_summary(p3ceq$cc_subscale, "Care coordination subscale (CC)", 15)
) |>
  mutate(across(c(Mean, Median, SD), \(x) round(x, 1))) |>
  kable(align = "lrrrrr")
```

```{r}
#| label: fig-p3ceq-total-dist
#| fig-cap: "Distribution of P3CEQ total scores (0–30, higher = more person-centred)"

p3ceq |>
  filter(!is.na(total)) |>
  ggplot(aes(total)) +
  geom_histogram(binwidth = 2, boundary = 0, fill = pal_blue, colour = "white", linewidth = 0.3) +
  scale_x_continuous(limits = c(0, 30), breaks = seq(0, 30, 5)) +
  labs(x = "P3CEQ total score", y = "Respondents", title = "P3CEQ total score distribution")
```

### Care coordination subscale vs PaRIS 2023

cohealth Kensington general practice previously conducted the P3CEQ survey in 2023 as part of PaRIS [ACSQHC, -@paris].
193 patients aged 45+ years of the cohealth Kensington clinic returned a PaRIS survey.

PaRIS reported the P3CEQ care coordination (CC) subscale breakdown, comparing Kensington's own patients
against a national comparison group (see `P3CEQ coordinated care subscale PaRIS 2023.png`).

```{r}
cc_bands <- c("Very low (0–3)", "Low (3.01–6)", "Moderate (6.01–9)", "High (9.01–12)", "Very high (12.01–15)")

# Reference percentages read off "P3CEQ coordinated care subscale PaRIS 2023.png" - no digital
# source for these exists, only that chart image (Kensington's 2023 PaRIS results and the PaRIS
# national comparison group). Average scores from the same image: 8.8 (Kensington 2023, Moderate)
# and 9.8 (PaRIS comparison 2023).
cc_paris_2023 <- tibble(
  band = factor(cc_bands, levels = cc_bands),
  `Kensington 2023`        = c(10, 19, 24, 23, 24),
  `PaRIS comparison 2023`  = c(6, 14, 24, 33, 23)
)

band_of_cc <- function(x) cut(x, breaks = c(0, 3, 6, 9, 12, 15), labels = cc_bands, include.lowest = TRUE)

cc_2026_data <- p3ceq |>
  left_join(survey |> select(KEY, q26), by = "KEY") |>
  filter(q26 %in% c(3, 4), !is.na(cc_subscale)) # age 45-64 (3) or 65+ (4), per q26opts

cc_2026_bands <- cc_2026_data |>
  mutate(band = band_of_cc(cc_subscale)) |>
  count(band, .drop = FALSE) |>
  mutate(`Kensington 2026` = n / sum(n) * 100) |>
  select(band, `Kensington 2026`)

cc_compare <- cc_paris_2023 |>
  left_join(cc_2026_bands, by = "band") |>
  pivot_longer(-band, names_to = "series", values_to = "pct") |>
  mutate(series = factor(series, levels = c("Kensington 2023", "PaRIS comparison 2023", "Kensington 2026")))
```

```{r}
#| label: cc-subscale-avg

avg_cc_2026 <- mean(cc_2026_data$cc_subscale)
n_cc_2026   <- nrow(cc_2026_data)
```

Average P3CEQ care coordination subscale score among respondents aged 45+ (n = `r n_cc_2026`) was
**`r round(avg_cc_2026, 1)` ** (`r band_of_cc(avg_cc_2026)`) for Kensington 2026.
This compares to 8.8 (Moderate) for Kensington 2023 and 9.8 for the PaRIS 2023 comparison group.

```{r}
#| label: fig-cc-subscale-paris
#| fig-cap: "P3CEQ care coordination subscale (0–15), patients aged 45+: Kensington 2026 vs PaRIS 2023"
#| fig-width: 8
#| fig-height: 4.5

ggplot(cc_compare, aes(pct, fct_rev(band), fill = series)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  geom_text(aes(label = paste0(round(pct), "%")), position = position_dodge(width = 0.75),
            hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_fill_manual(values = pal_cat[1:3]) +
  scale_x_continuous(limits = c(0, max(cc_compare$pct, na.rm = TRUE) * 1.15)) +
  labs(x = "Share of respondents aged 45+", y = NULL) +
  # legend reads top-down as Kensington 2026 / PaRIS comparison 2023 / Kensington 2023, matching
  # the dodge order of the bars themselves (series factor levels stay as-is - this only reorders
  # the legend keys, not the fill scale or bar positions)
  guides(fill = guide_legend(reverse = TRUE))
```

### Confidence to self-manage and person-centred care vs PaRIS10 Dashboard 2024

The OECD's PaRIS10 Dashboard [@oecd-paris] benchmarks two further P3CEQ-derived
measures for primary care users aged 45+ living with one or more chronic conditions:
**confidence to self-manage** (a single item — "how confident are you that you can manage your
own health and well-being?" — positive if confident/very confident) and **person-centred care**
(the PC subscale above, out of 24, positive if the score is 12 or more).

The Australia and OECD PaRIS figures below are age-sex standardised to the OECD PaRIS standard
population [@oecd-paris; @groenewegen2024]; Kensington's figures are standardised to the same
reference population (see [Notes](#sec-standardisation)).

```{r}
#| label: paris10-dashboard-compare

paris10_data <- p3ceq |>
  left_join(
    survey |>
      mutate(
        KEY, q22, q26,
        n_conditions = rowSums(across(matches("^q9_(1|2|3|4|5|6|7|8|9|10|11|12)$")), na.rm = TRUE),
        .keep = "none"
      ),
    by = "KEY"
  ) |>
  filter(q26 %in% c(3, 4), n_conditions >= 1) # age 45+ (per q26opts) with 1+ long-term condition

n_paris10          <- nrow(paris10_data)
n_paris10_nogender <- sum(is.na(paris10_data$q22)) # unanswered Q22 - excluded below, no stratum to assign

# ---- age-sex standardisation to the OECD PaRIS standard population -------------------------
# Table 7.5 of @oecd-paris (Section 7.7.2) gives the OECD-PaRIS standard population as two
# marginal distributions, not a joint age-by-sex table: age in four bands (45-54 25%, 55-64 28%,
# 65-74 27%, 75+ 20%) and sex (women 55%, men 45%). Kensington's q26 only distinguishes 45-64 vs
# 65+, so those OECD age bands are collapsed to match (45-64 -> 53%, 65+ -> 47%) and combined with
# sex assuming independence (the OECD report doesn't publish the cross-tabulation) into four
# stratum weights, used to directly reweight Kensington's own stratum estimates - the saturated
# special case of the re-centred-regression method in the PaRIS data analysis plan
# [@groenewegen2024].
oecd_std_weights <- tribble(
  ~q26, ~q22, ~std_weight,
  3,    1,    0.53 * 0.45, # 45-64, Male
  3,    2,    0.53 * 0.55, # 45-64, Female
  4,    1,    0.47 * 0.45, # 65+, Male
  4,    2,    0.47 * 0.55  # 65+, Female
)

paris10_strata <- paris10_data |>
  filter(!is.na(q22)) |>
  group_by(q26, q22) |>
  summarise(
    n          = n(),
    pct_conf   = mean(p10 >= 2, na.rm = TRUE) * 100, # p10 = recoded q19; 2="Confident", 3="Very confident"
    pct_pc_pos = mean(pc_subscale >= 12, na.rm = TRUE) * 100,
    avg_pc     = mean(pc_subscale, na.rm = TRUE),
    .groups = "drop"
  ) |>
  left_join(oecd_std_weights, by = c("q26", "q22"))

standardise <- function(x) weighted.mean(x, paris10_strata$std_weight)

pct_conf_2026_std   <- standardise(paris10_strata$pct_conf)
pct_pc_pos_2026_std <- standardise(paris10_strata$pct_pc_pos)
avg_pc_2026_std     <- standardise(paris10_strata$avg_pc)

# Crude (unstandardised) figures, kept for reference alongside the standardised ones above.
avg_pc_2026     <- mean(paris10_data$pc_subscale, na.rm = TRUE)
pct_pc_pos_2026 <- mean(paris10_data$pc_subscale >= 12, na.rm = TRUE) * 100
pct_conf_2026   <- mean(paris10_data$p10 >= 2, na.rm = TRUE) * 100

# Australia and OECD PaRIS figures are read directly off "PaRIS OECD PaRIS10 Dashboard.png"
# (Table 2.2, OECD "Does Healthcare Deliver?" report [@oecd-paris]) - the % reporting a positive
# outcome for each measure, among primary care users aged 45+ with 1+ chronic condition, age-sex
# standardised to the OECD PaRIS standard population; Kensington's figures below are standardised
# the same way (see above).
paris10_compare <- tribble(
  ~measure,                    ~series,                   ~pct,
  "Confidence to self-manage", "Kensington 2026",         pct_conf_2026_std,
  "Confidence to self-manage", "Australia (PaRIS 2024)",  61,
  "Confidence to self-manage", "OECD PaRIS (2024)",       59,
  "Person-centred care",       "Kensington 2026",         pct_pc_pos_2026_std,
  "Person-centred care",       "Australia (PaRIS 2024)",  93,
  "Person-centred care",       "OECD PaRIS (2024)",       87
) |>
  mutate(
    series  = factor(series, levels = c("Kensington 2026", "Australia (PaRIS 2024)", "OECD PaRIS (2024)")),
    measure = factor(measure, levels = c("Confidence to self-manage", "Person-centred care"))
  )
```

Among respondents aged 45+ with a long-term condition (n = `r n_paris10`; `r n_paris10_nogender`
did not answer Q22 and are excluded from standardisation), age-sex standardised to the OECD PaRIS
standard population:

- **Confidence to self-manage**: `r round(pct_conf_2026_std)`% reported being confident or very
  confident in managing their own health and well-being (`r round(pct_conf_2026)`% unstandardised),
  compared with 61% for Australia and 59% for the OECD PaRIS average.
- **Person-centred care**: average PC subscale score `r round(avg_pc_2026_std, 1)` out of 24
  (`r round(pct_pc_pos_2026_std)`% scoring 12 or more, i.e. a "positive" experience; unstandardised:
  `r round(avg_pc_2026, 1)`, `r round(pct_pc_pos_2026)`%), compared with 18.1 (93%) for Australia
  and 16.6 (87%) for the OECD PaRIS average.

```{r}
#| label: fig-paris10-dashboard
#| fig-cap: "Confidence to self-manage and person-centred care vs PaRIS10 Dashboard 2024, patients aged 45+ with 1+ chronic condition (age-sex standardised)"
#| fig-width: 8
#| fig-height: 4.5

ggplot(paris10_compare, aes(series, pct, fill = series)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = paste0(round(pct), "%")), vjust = -0.4, size = 3.5, colour = ink_secondary) +
  facet_wrap(~measure) +
  scale_fill_manual(values = pal_cat[1:3]) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(x = NULL, y = "Share reporting a positive outcome") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 20, hjust = 1))
```

### Item-level results

```{r}
#| label: fig-p3ceq-items
#| fig-cap: "Mean score per P3CEQ item (0–3 scale, higher = better)"
#| fig-height: 5

p3ceq_item_labels <- c(
  p1  = "Q1. Discussed what matters to you",
  p2  = "Q2. Involved in decisions about your care",
  p3  = "Q3. Considered as a whole person",
  p4  = "Q4. Didn't have to repeat information*",
  p5  = "Q5. Healthcare joined up / works for you",
  p6  = "Q6. Has a single coordinating professional",
  p7  = "Q7. Care plan in place and followed (avg of 7a–7d)",
  p8  = "Q8. Enough support to manage own health",
  p9  = "Q9. Useful information when needed",
  p10 = "Q10. Confident managing own health"
)

p3ceq |>
  select(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10) |>
  pivot_longer(everything(), names_to = "item", values_to = "score") |>
  filter(!is.na(score)) |>
  group_by(item) |>
  summarise(mean_score = mean(score), n = n(), .groups = "drop") |>
  mutate(item = fct_reorder(p3ceq_item_labels[item], mean_score)) |>
  ggplot(aes(mean_score, item)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = number(mean_score, accuracy = 0.1)),
            hjust = -0.3, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, 3.4), breaks = 0:3) +
  labs(x = "Mean score (0–3)", y = NULL,
       title = "P3CEQ item scores",
       subtitle = "*Q4 is reverse-scored: a high score means information rarely had to be repeated")
```

## RACGP administrative staff, privacy and continuity of care

Questions 1–3 are selected questions from the [@racgppatientfeedbackguide]. The questions chosen
focused on the communication and interpersonal skills of administrative staff,
privacy and confidentiality and continuity of care, with a focus on care coordination.
Each question is rated on a 5-point Poor–Excellent scale (with "N/A" and "Don't
know" excluded from the summaries below).

```{r}
#| label: fig-rate7-items
#| fig-cap: "Reception, privacy and clinician coordination — response distribution (valid responses only)"
#| fig-width: 9
#| fig-height: 5.5

rate7_labs <- choice_labels("rate7")
rate7_valid <- names(rate7_labs)[!rate7_labs %in% c("N/A", "Don't know")]

rate7_vars <- c("q1a", "q1b", "q1c", "q2a", "q2b", "q2c", "q3a", "q3b", "q3c", "q3d")

rate7_long <- survey |>
  select(all_of(rate7_vars)) |>
  mutate(across(everything(), as.character)) |>
  pivot_longer(everything(), names_to = "var", values_to = "value") |>
  filter(value %in% rate7_valid) |>
  mutate(
    item = fct_rev(fct_inorder(map_chr(var, item_label))),
    response = factor(rate7_labs[value], levels = rate7_labs[rate7_valid])
  )

rate7_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(pct, item, fill = response)) +
  geom_col(width = 0.7, position = position_stack(reverse = TRUE)) +
  scale_fill_manual(values = pal_seq) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
  labs(x = "Share of valid responses", y = NULL, title = "Ratings by item") +
  theme(legend.position = "top")
```

Patients were invited to 'free-text' comment on their experience with reception, privacy
and coordination. These comments can be read in
[What patients said](#sec-comment_racgp_q).

## Long-term conditions

```{r}
#| label: fig-conditions
#| fig-cap: "Long-term conditions reported by respondents"
#| fig-width: 8
#| fig-height: 7

summarise_multiselect <- function(data, prefix, list_name) {
  labs <- choice_labels(list_name)
  cols <- data |> select(matches(paste0("^", prefix, "_[0-9]+$")))
  tibble(
    value = str_remove(names(cols), paste0("^", prefix, "_")),
    n = colSums(cols, na.rm = TRUE)
  ) |>
    mutate(label = labs[value], pct = n / nrow(data)) |>
    arrange(desc(n))
}

# Unlike summarise_multiselect() above (one bar per option, so a respondent who selected several
# options is counted on several bars), this gives each respondent's full combination of selected
# options its own bar - needed for Q28, where holding more than one concession card is common and
# would otherwise be double-counted across the individual-card bars.
summarise_multiselect_combos <- function(data, prefix, list_name) {
  labs <- choice_labels(list_name)
  cols <- data |> select(matches(paste0("^", prefix, "_[0-9]+$")))
  values <- str_remove(names(cols), paste0("^", prefix, "_"))
  mat <- as.matrix(cols)
  mat[is.na(mat)] <- 0
  combo <- apply(mat, 1, function(row) {
    selected <- values[row == 1]
    if (length(selected) == 0) return(NA_character_) # skipped the question entirely
    paste(labs[selected], collapse = " + ")
  })
  tibble(label = combo) |>
    filter(!is.na(label)) |>
    count(label, name = "n") |>
    mutate(pct = n / nrow(data)) |>
    arrange(desc(n))
}

conditions <- summarise_multiselect(survey, "q9", "conditions")

conditions |>
  mutate(label = fct_reorder(str_wrap(label, 28), n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(conditions$n) * 1.15)) +
  labs(x = "Respondents", y = NULL, title = "Long-term conditions (Q9)",
       subtitle = paste0("Out of ", n_consented, " respondents; multiple selections allowed"))
```

Q9 also lets respondents specify "Other long-term condition(s)" as free text. `q9_other` holds
what respondents typed in; below are those responses as given, one row per respondent.

```{r}
#| label: tbl-conditions-other
#| tbl-cap: "Q9 \"Other long-term condition(s)\": free-text responses"

other_conditions <- survey |>
  mutate(q9_other = str_squish(q9_other)) |>
  filter(!is.na(q9_other), q9_other != "") |>
  mutate(`Free-text response` = q9_other, .keep = "none")

kable(other_conditions, align = "l")
```

`r nrow(other_conditions)` free-text responses, out of `r conditions$n[conditions$label == "Other long-term condition(s) (please specify)"]`
respondents who selected "Other long-term condition(s)".

### Multiple chronic conditions vs PaRIS 2025

The 2025 PaRIS Australian national report states that 64% of patients aged 45+ reported having
at least one chronic condition [ACSQHC, -@paris].

```{r}
#| label: fig-any-condition
#| fig-cap: "Any long-term condition, respondents aged 45+: Kensington 2026 vs PaRIS Australia 2025"
#| fig-width: 5
#| fig-height: 3

# Number of conditions = count of actual conditions ticked in Q9 (q9_1..q9_12), excluding the
# "I have never been told..." option (q9_13, not a condition).
num_conditions <- survey |>
  mutate(
    KEY,
    n_conditions = rowSums(across(matches("^q9_(1|2|3|4|5|6|7|8|9|10|11|12)$")), na.rm = TRUE),
    age_group = case_when(
      q26 %in% c(1, 2) ~ "under45",
      q26 %in% c(3, 4) ~ "45plus",
      TRUE             ~ "unspecified" # q26 == 5 ("Don't wish to say") or blank
    ),
    .keep = "none"
  )

n_45plus_total <- sum(num_conditions$age_group == "45plus")
n_45plus_any   <- sum(num_conditions$age_group == "45plus" & num_conditions$n_conditions >= 1)
pct_45plus_any <- n_45plus_any / n_45plus_total * 100

any_condition_compare <- tibble(
  series = factor(c("Kensington 2026", "Australia (PaRIS 2025)"),
                   levels = c("Kensington 2026", "Australia (PaRIS 2025)")),
  pct = c(pct_45plus_any, 64) # Australia figure quoted directly in "PaRIS 2025 Australia chronic conditions.png"
)

any_condition_compare |>
  ggplot(aes(series, pct)) +
  geom_col(fill = pal_blue, width = 0.5) +
  geom_text(aes(label = paste0(round(pct), "%")), vjust = -0.4, size = 4.5, colour = ink_secondary) +
  scale_y_continuous(limits = c(0, max(any_condition_compare$pct) * 1.15)) +
  labs(x = NULL, y = "Share of respondents aged 45+\nwith 1+ long-term condition")
```

In this survey, `r n_45plus_any` of `r n_45plus_total` respondents aged 45+ (`r round(pct_45plus_any)`%)
from cohealth Kensington report at least one long-term condition, vs. 64% in the PaRIS Australia 2025 report.

@oecd-paris describes the number of reported chronic conditions per patient, 
among patients aged 45+ report who report having at least one condition.
Australian and OECD figures are compared below to survey respondents from cohealth Kensington 2026, split by age band.

```{r}
#| label: fig-multiple-conditions
#| fig-cap: "Number of long-term conditions, among respondents reporting at least one"
#| fig-width: 9
#| fig-height: 6

n_kensington <- num_conditions |>
  filter(n_conditions >= 1) |>
  count(age_group, name = "n_group")

kensington_dist <- num_conditions |>
  filter(n_conditions >= 1) |>
  mutate(n_conditions = pmin(n_conditions, 6)) |>
  count(age_group, n_conditions) |>
  left_join(n_kensington, by = "age_group") |>
  mutate(pct = n / n_group * 100) |>
  select(age_group, n_conditions, pct, n_group)

age_group_labels <- c(
  `45plus`      = paste0("Kensington 2026, 45+ (n=", n_kensington$n_group[n_kensington$age_group == "45plus"], ")"),
  under45       = paste0("Kensington 2026, under 45 (n=", n_kensington$n_group[n_kensington$age_group == "under45"], ")"),
  unspecified   = paste0("Kensington 2026, age not stated (n=", n_kensington$n_group[n_kensington$age_group == "unspecified"], ")")
)

kensington_long <- kensington_dist |>
  mutate(series = age_group_labels[age_group]) |>
  select(series, n_conditions, pct)

# Read off "PaRIS 2025 multiple chronic conditions.png" by measuring the stacked-bar segment
# widths for the Australia and OECD PaRIS rows (no digital source for the underlying values was
# available - the chart has no printed data labels) - approximate to the nearest whole percent.
paris_2025 <- tribble(
  ~series,                    ~n_conditions, ~pct,
  "Australia (PaRIS 2025)",   1,             27,
  "Australia (PaRIS 2025)",   2,             30,
  "Australia (PaRIS 2025)",   3,             23,
  "Australia (PaRIS 2025)",   4,             13,
  "Australia (PaRIS 2025)",   5,             5,
  "Australia (PaRIS 2025)",   6,             2,
  "OECD average (PaRIS 2025)",1,             35,
  "OECD average (PaRIS 2025)",2,             30,
  "OECD average (PaRIS 2025)",3,             19,
  "OECD average (PaRIS 2025)",4,             10,
  "OECD average (PaRIS 2025)",5,             4,
  "OECD average (PaRIS 2025)",6,             2
)

series_order <- c(age_group_labels[c("45plus", "under45", "unspecified")],
                   "Australia (PaRIS 2025)", "OECD average (PaRIS 2025)")

conditions_compare <- bind_rows(kensington_long, paris_2025) |>
  mutate(
    series = factor(series, levels = series_order),
    n_conditions = factor(n_conditions, levels = 1:6, labels = c("1", "2", "3", "4", "5", "6 or more"))
  )

conditions_compare |>
  ggplot(aes(n_conditions, pct)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = paste0(round(pct), "%")), vjust = -0.4, size = 3, colour = ink_secondary) +
  scale_y_continuous(limits = c(0, max(conditions_compare$pct, na.rm = TRUE) * 1.15),
                      expand = expansion(mult = c(0, 0.02))) +
  facet_wrap(~series, ncol = 3) +
  labs(x = "Number of long-term conditions", y = "Share of respondents with 1+ condition") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing = unit(1.2, "lines"))
```

### Most reported chronic conditions vs PaRIS 2025

ACSQHC [-@paris] compares the specific chronic conditions reported among Australia
and OECD patients aged 45+ (and who report at least one chronic condition).
These statistics are compared to Kensington respondents aged 45+ with 1+ condition 
(`r n_45plus_any` survey respondents).

```{r}
#| label: fig-conditions-paris
#| fig-cap: "Most reported chronic conditions, respondents aged 45+ with 1+ condition: Kensington 2026 vs PaRIS 2025"
#| fig-width: 9
#| fig-height: 8

# Maps each Q9 "conditions" choice value to the matching row in the PaRIS Figure 1 chart, in that
# chart's own order (largest-to-smallest by the Australia figure).
condition_labels_paris <- c(
  `1`  = "High blood pressure",
  `4`  = "Arthritis or ongoing back / joint problems",
  `7`  = "Depression, anxiety or other mental health conditions",
  `5`  = "Breathing conditions",
  `2`  = "Cardiovascular / heart conditions",
  `3`  = "Diabetes (Type 1 or 2)",
  `11` = "Cancer (diagnosis / treatment in the past 5 years)",
  `8`  = "Neurological conditions",
  `9`  = "Chronic kidney disease",
  `10` = "Chronic liver disease",
  `6`  = "Alzheimer's disease / other causes of dementia",
  `12` = "Other long-term health condition(s)"
)
condition_order_paris <- unname(condition_labels_paris)

base_45plus_any <- num_conditions |> filter(age_group == "45plus", n_conditions >= 1) |> pull(KEY)

kensington_conditions_paris <- survey |>
  filter(KEY %in% base_45plus_any) |>
  select(all_of(paste0("q9_", names(condition_labels_paris)))) |>
  summarise(across(everything(), \(x) mean(x, na.rm = TRUE) * 100)) |>
  pivot_longer(everything(), names_to = "value", values_to = "pct") |>
  mutate(
    value = str_remove(value, "^q9_"),
    label = condition_labels_paris[value],
    series = paste0("Kensington 2026 (n=", length(base_45plus_any), ")")
  ) |>
  select(label, series, pct)

# Percentages printed directly on the bars in "PaRIS 2025 Australia chronic conditions.png" -
# read exactly from the chart, not estimated.
conditions_paris_2025 <- tribble(
  ~label,                                                    ~series,                     ~pct,
  "High blood pressure",                                     "Australia (PaRIS 2025)",    57,
  "High blood pressure",                                     "OECD average (PaRIS 2025)", 53,
  "Arthritis or ongoing back / joint problems",               "Australia (PaRIS 2025)",    45,
  "Arthritis or ongoing back / joint problems",               "OECD average (PaRIS 2025)", 37,
  "Depression, anxiety or other mental health conditions",    "Australia (PaRIS 2025)",    33,
  "Depression, anxiety or other mental health conditions",    "OECD average (PaRIS 2025)", 16,
  "Breathing conditions",                                     "Australia (PaRIS 2025)",    24,
  "Breathing conditions",                                     "OECD average (PaRIS 2025)", 17,
  "Cardiovascular / heart conditions",                        "Australia (PaRIS 2025)",    23,
  "Cardiovascular / heart conditions",                        "OECD average (PaRIS 2025)", 21,
  "Diabetes (Type 1 or 2)",                                   "Australia (PaRIS 2025)",    16,
  "Diabetes (Type 1 or 2)",                                   "OECD average (PaRIS 2025)", 19,
  "Cancer (diagnosis / treatment in the past 5 years)",       "Australia (PaRIS 2025)",    11,
  "Cancer (diagnosis / treatment in the past 5 years)",       "OECD average (PaRIS 2025)", 9,
  "Neurological conditions",                                  "Australia (PaRIS 2025)",    9,
  "Neurological conditions",                                  "OECD average (PaRIS 2025)", 7,
  "Chronic kidney disease",                                   "Australia (PaRIS 2025)",    4,
  "Chronic kidney disease",                                   "OECD average (PaRIS 2025)", 3,
  "Chronic liver disease",                                    "Australia (PaRIS 2025)",    2,
  "Chronic liver disease",                                    "OECD average (PaRIS 2025)", 2,
  "Alzheimer's disease / other causes of dementia",           "Australia (PaRIS 2025)",    1,
  "Alzheimer's disease / other causes of dementia",           "OECD average (PaRIS 2025)", 1,
  "Other long-term health condition(s)",                      "Australia (PaRIS 2025)",    21,
  "Other long-term health condition(s)",                      "OECD average (PaRIS 2025)", 25
)

conditions_paris_series <- c(unique(kensington_conditions_paris$series),
                              "Australia (PaRIS 2025)", "OECD average (PaRIS 2025)")

conditions_paris_compare <- bind_rows(kensington_conditions_paris, conditions_paris_2025) |>
  mutate(
    label = factor(label, levels = rev(condition_order_paris)),
    series = factor(series, levels = conditions_paris_series)
  )

ggplot(conditions_paris_compare, aes(pct, label, fill = series)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  geom_text(aes(label = paste0(round(pct), "%")), position = position_dodge(width = 0.75),
            hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_fill_manual(values = pal_cat[1:3]) +
  scale_x_continuous(limits = c(0, max(conditions_paris_compare$pct, na.rm = TRUE) * 1.15)) +
  labs(x = "Share of respondents aged 45+ with 1+ condition", y = NULL) +
  # legend reads top-down as OECD, Australia, Kensington 2026, matching
  # the dodge order of the bars themselves (series factor levels stay as-is - this only reorders
  # the legend keys, not the fill scale or bar positions)
  guides(fill = guide_legend(reverse = TRUE))
```

### Care coordination by number of conditions

#### P3CEQ subscales

The chart below is restricted to respondents who answered Q9 (so "0" is a real answer of no
long-term conditions, not a skipped question), with no age restriction — unlike the 45+ comparisons
against PaRIS benchmarks earlier, every respondent who answered Q9 is included regardless of age. It
compares the P3CEQ person-centred (PC, out of 24) and care coordination (CC, out of 15) subscale
scores against the number of long-term conditions reported.

```{r}
#| label: p3ceq-subscales-by-conditions
#| fig-cap: "P3CEQ PC and CC subscale scores by number of long-term conditions (Q9)"
#| fig-width: 8
#| fig-height: 4.5

# The exploded q9_* indicator columns are 0 (not NA) even when Q9 was skipped entirely - SurveyCTO
# fills them in regardless - so "answered" has to be read off the raw q9 column (a space-separated
# list of selected codes, empty string when skipped) rather than off the indicator columns. A
# respondent who answered and selected only "never been told by a doctor..." (q9_13) is a real
# answer of zero conditions; one who left q9 blank is not and must be excluded, not counted as zero.
q9_conditions <- survey |>
  mutate(
    KEY,
    answered_q9 = !is.na(q9) & q9 != "",
    n_conditions = rowSums(across(matches("^q9_(1|2|3|4|5|6|7|8|9|10|11|12)$")), na.rm = TRUE),
    condition_band = factor(pmin(n_conditions, 5), levels = 0:5,
                             labels = c("0", "1", "2", "3", "4", "5+")),
    .keep = "none"
  ) |>
  filter(answered_q9)

subscale_labels <- c(
  pc_subscale = "Person-centred (PC, out of 24)",
  cc_subscale = "Care coordination (CC, out of 15)"
)

# PC and CC are on different maximum scores (24 vs 15), so they're faceted with independent y-axes
# rather than drawn as two lines on one shared axis.
subscale_by_conditions <- p3ceq |>
  select(KEY, pc_subscale, cc_subscale) |>
  inner_join(q9_conditions, by = "KEY") |>
  pivot_longer(c(pc_subscale, cc_subscale), names_to = "subscale", values_to = "score") |>
  filter(!is.na(score)) |>
  mutate(subscale = factor(subscale_labels[subscale], levels = subscale_labels))

subscale_summary <- subscale_by_conditions |>
  group_by(condition_band, subscale) |>
  summarise(mean_score = mean(score), n = n(), .groups = "drop")

ggplot(subscale_summary, aes(condition_band, mean_score, group = subscale)) +
  geom_line(linewidth = 0.9, colour = pal_blue) +
  geom_point(size = 2.5, colour = pal_blue) +
  facet_wrap(~subscale, scales = "free_y") +
  labs(x = "Number of long-term conditions (Q9)", y = "Mean subscale score",
       title = "P3CEQ subscale scores by number of long-term conditions") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0))
```

#### RACGP care continuity and coordination questions

The same Q9-answered group is compared against the four care continuity and coordination items
from the [RACGP patient feedback guide, -@racgppatientfeedbackguide]:
"knew your medical history", "the clinician was aware of advice you had received from other health
professionals", "coordinated different healthcare professionals" and "gave the right amount of
information to other healthcare professionals". As in [Clinic-specific
experience](#clinic-specific-experience), "N/A" and "Don't know" responses are excluded.

```{r}
#| label: rate7-q3-by-conditions
#| fig-cap: "Q3 clinic-specific coordination items by number of long-term conditions (Q9)"
#| fig-width: 8
#| fig-height: 5

q3_vars <- c("q3a", "q3b", "q3c", "q3d")

q3_item_labels <- c(
  q3a = "Knew your medical history",
  q3b = "Aware of advice from other health professionals",
  q3c = "Coordinated different healthcare professionals",
  q3d = "Gave the right amount of information to other professionals"
)

q3_by_conditions <- survey |>
  select(KEY, all_of(q3_vars)) |>
  inner_join(q9_conditions, by = "KEY") |>
  mutate(across(all_of(q3_vars), ~ if_else(.x %in% 1:5, .x, NA_real_))) # drop N/A (6) / Don't know (7)

q3_summary <- q3_by_conditions |>
  select(condition_band, all_of(q3_vars)) |>
  pivot_longer(-condition_band, names_to = "item", values_to = "rating") |>
  filter(!is.na(rating)) |>
  group_by(condition_band, item) |>
  summarise(mean_rating = mean(rating), n = n(), .groups = "drop") |>
  mutate(item = factor(q3_item_labels[item], levels = q3_item_labels))

ggplot(q3_summary, aes(condition_band, mean_rating, colour = item, group = item)) +
  geom_line(linewidth = 0.9) +
  geom_point(size = 2.5) +
  scale_colour_manual(values = pal_cat[1:4], labels = \(x) str_wrap(x, 28)) +
  scale_y_continuous(limits = c(1, 5), breaks = 1:5) +
  labs(x = "Number of long-term conditions (Q9)", y = "Mean rating (1 = Poor, 5 = Excellent)",
       title = "Clinic-specific coordination items (Q3) by number of long-term conditions") +
  # four long labels don't fit on one legend row without running off the right edge of the
  # figure (only 3 of the 4 series were visible) - force two rows so all four are shown
  guides(colour = guide_legend(nrow = 2, byrow = TRUE))
```

## Respondent profile

```{r}
#| label: fig-demographics
#| fig-cap: "Respondent demographics"
#| fig-width: 11
#| fig-height: 12

demo_vars <- tribble(
  ~var, ~list, ~title,
  "q22", "q22opts", "Gender (Q22)",
  "q26", "q26opts", "Age (Q26)",
  "q27", "q27opts", "Time at this practice (Q27)",
  "q29", "q29opts", "Visits in past 12 months (Q29)",
  "q30", "q30opts", "Highest education level (Q30)",
  "q31", "q31opts", "Visit was for self or someone else (Q31)",
  "q23", "yesno",   "Aboriginal/Torres Strait Islander (Q23)",
  "q24", "yesno",   "Attended another GP practice in past year (Q24)"
)

demo_long <- pmap_dfr(demo_vars, function(var, list, title) {
  labs <- choice_labels(list)
  survey |>
    mutate(value = as.character(.data[[var]])) |>
    filter(!is.na(value), value %in% names(labs)) |>
    count(value) |>
    mutate(
      question = title,
      response = factor(labs[value], levels = labs),
      pct = n / sum(n)
    )
})

demo_long |>
  ggplot(aes(pct, fct_rev(response))) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 1)), hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.25))) +
  facet_wrap(~question, scales = "free_y", ncol = 2) +
  labs(x = NULL, y = NULL, title = "Who responded") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

```{r}
#| label: demographics-extra

languages <- summarise_multiselect(survey, "q25", "languages")
# Combination-based, not per-card: several respondents hold more than one concession card (e.g.
# both a Health Care Card and a Pensioner Concession Card), so each held combination gets its own
# bar rather than counting that respondent once per card.
concession <- summarise_multiselect_combos(survey, "q28", "q28opts")
```

```{r}
#| label: fig-languages
#| fig-cap: "Languages spoken at home (Q25) and concession cards held (Q28, by combination held)"
#| fig-width: 10
#| fig-height: 4.5

bind_rows(
  languages |> mutate(facet = "Languages spoken at home (Q25)"),
  concession |> mutate(facet = "Concession cards held (Q28)")
) |>
  mutate(label = fct_reorder(str_wrap(label, 30), n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.2, colour = ink_secondary) +
  facet_wrap(~facet, scales = "free", ncol = 2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Respondents", y = NULL) +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

A large share of the Q25 "Other" responses come from a wide mix of languages.
`q25_other` holds what respondents typed in; below are those free-text responses
as given (grouped only where the text matches exactly), most-common first.

```{r}
#| label: fig-languages-other
#| fig-cap: "Q25 'Other' responses: languages named in free text"
#| fig-width: 7
#| fig-height: 4

other_langs <- survey |>
  mutate(q25_other = str_squish(q25_other)) |>
  filter(!is.na(q25_other), q25_other != "") |>
  count(q25_other, sort = TRUE)

other_langs |>
  mutate(q25_other = fct_reorder(q25_other, n)) |>
  ggplot(aes(n, q25_other)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(other_langs$n) * 1.15), breaks = scales::breaks_pretty()) +
  labs(x = "Respondents", y = NULL, title = "Q25 \"Other\": languages named in free text",
       subtitle = paste0(sum(other_langs$n), " free-text responses, out of ",
                          languages$n[languages$label == "Other"], " respondents who selected \"Other\""))
```

### P3CEQ subscales by language spoken at home

The chart below is restricted to respondents who answered Q25 and who recorded at least one
long-term condition in Q9 (per `q9_conditions` above, so a Q9 skip is excluded rather than counted
as zero conditions), with no age restriction. Respondents are grouped into three categories based
on the individual Q25 language options: "English only" (selected English, `q25_1`, and no other language),
"Another language (no English)" (selected at least one other language and not English),
and "English and another language" (selected both).

```{r}
#| label: p3ceq-subscales-by-language
#| fig-cap: "P3CEQ PC and CC subscale scores by language spoken at home (Q25), respondents with 1+ long-term conditions (Q9)"
#| fig-width: 8
#| fig-height: 4.5

language_group_levels <- c("English only", "Another language (no English)", "English and another language")

# The exploded q25_* indicator columns are 0 (not NA) even when Q25 was skipped entirely -
# SurveyCTO fills them in regardless - so "answered" has to be read off the raw q25 column (NA when
# skipped) rather than off the indicator columns. Once answered_q25 is TRUE, q25_1 is a real 0/1.
q25_language <- survey |>
  mutate(
    KEY,
    answered_q25 = !is.na(q25) & q25 != "",
    has_english  = q25_1 == 1,
    has_other    = rowSums(across(matches("^q25_[2-8]$")), na.rm = TRUE) > 0,
    language_group = factor(case_when(
      has_english & !has_other ~ "English only",
      !has_english & has_other ~ "Another language (no English)",
      has_english & has_other  ~ "English and another language"
    ), levels = language_group_levels),
    .keep = "none"
  ) |>
  filter(answered_q25)

# subscale_labels and q9_conditions defined earlier in "P3CEQ subscales by number of conditions"
# above; q9_conditions is already restricted to respondents who answered Q9.
subscale_by_language <- p3ceq |>
  select(KEY, pc_subscale, cc_subscale) |>
  inner_join(q25_language, by = "KEY") |>
  inner_join(q9_conditions |> select(KEY, n_conditions), by = "KEY") |>
  filter(n_conditions >= 1) |>
  pivot_longer(c(pc_subscale, cc_subscale), names_to = "subscale", values_to = "score") |>
  filter(!is.na(score)) |>
  mutate(subscale = factor(subscale_labels[subscale], levels = subscale_labels))

language_summary <- subscale_by_language |>
  group_by(language_group, subscale) |>
  summarise(mean_score = mean(score), n = n(), .groups = "drop")

ggplot(language_summary, aes(language_group, mean_score)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = number(mean_score, accuracy = 0.1)), vjust = -0.5, size = 3.3, colour = ink_secondary) +
  facet_wrap(~subscale, scales = "free_y") +
  scale_x_discrete(labels = \(x) str_wrap(x, 12)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(x = NULL, y = "Mean subscale score",
       title = "P3CEQ subscale scores by language spoken at home") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0))
```

### Predictors of P3CEQ scores: language, gender, age and number of chronic conditions

Multiple linear regression estimates the association of language spoken at home (Q25), gender
(Q22), age band (Q26) and number of long-term conditions (Q9, entered as a linear term) with the
P3CEQ total score and PC/CC subscales. The sample is restricted to respondents who recorded
at least one long-term condition in Q9, and who answered Q25, Q22 and Q26 — a "Don't wish to say"
age response (Q26 = 5) is treated as not having answered an age. Each outcome's model
uses every respondent in that sample with a non-missing score for it, so the
total, PC and CC models can have slightly different sample sizes.

```{r}
#| label: p3ceq-regression

# Age band collapses Q26's five options into three: "Don't wish to say" (5) and a blank answer are
# excluded (not an age), and the sparse 15-24 and 25-44 bands (2 and 11 respondents respectively,
# among those with 1+ condition) are combined into "Under 45" so the model isn't fit on near-empty
# cells.
demo_covariates <- survey |>
  mutate(
    KEY,
    gender = factor(case_when(q22 == 1 ~ "Male", q22 == 2 ~ "Female"), levels = c("Female", "Male")),
    age_band = factor(case_when(
      q26 %in% c(1, 2) ~ "Under 45",
      q26 == 3          ~ "45–64",
      q26 == 4          ~ "65+"
    ), levels = c("Under 45", "45–64", "65+")),
    .keep = "none"
  ) |>
  filter(!is.na(gender), !is.na(age_band))

# q25_language and q9_conditions defined earlier above; both are already restricted to respondents
# who answered Q25 / Q9 respectively.
reg_data <- p3ceq |>
  select(KEY, total, pc_subscale, cc_subscale) |>
  inner_join(q9_conditions |> filter(n_conditions >= 1) |> select(KEY, n_conditions), by = "KEY") |>
  inner_join(q25_language |> select(KEY, language_group), by = "KEY") |>
  inner_join(demo_covariates, by = "KEY")

reg_outcome_labels <- c(
  total       = "P3CEQ total (0–30)",
  pc_subscale = "PC subscale (0–24)",
  cc_subscale = "CC subscale (0–15)"
)

# lm()'s default na.action (na.omit) drops rows missing that particular outcome, so each model
# fits on all of reg_data with a non-missing score for it - no separate per-outcome filter needed.
reg_predictors <- c("language_group", "gender", "age_band", "n_conditions")
reg_models <- map(names(reg_outcome_labels), function(outcome) {
  lm(reformulate(reg_predictors, response = outcome), data = reg_data)
}) |>
  set_names(names(reg_outcome_labels))

reg_term_labels <- c(
  "(Intercept)" = "Intercept (English only, Female, Under 45, 0 conditions)",
  "language_groupAnother language (no English)" = "Another language (no English)",
  "language_groupEnglish and another language"   = "English and another language",
  "genderMale"          = "Male",
  "age_band45–64"  = "45–64",
  "age_band65+"         = "65+",
  "n_conditions"        = "Number of conditions (Q9, per condition)"
)

reg_coefs <- map_dfr(names(reg_models), function(nm) {
  broom::tidy(reg_models[[nm]], conf.int = TRUE) |>
    mutate(outcome = reg_outcome_labels[[nm]], n = nobs(reg_models[[nm]]))
}) |>
  mutate(
    outcome = factor(outcome, levels = reg_outcome_labels),
    term = factor(reg_term_labels[term], levels = rev(reg_term_labels))
  )
```

```{r}
#| label: fig-p3ceq-regression
#| fig-cap: "Predictors of P3CEQ scores: language, gender, age and number of conditions (95% CI), among respondents with 1+ long-term conditions (Q9)"
#| fig-width: 9
#| fig-height: 5.5

reg_coefs |>
  filter(term != "Intercept (English only, Female, Under 45, 0 conditions)") |>
  ggplot(aes(estimate, term)) +
  geom_vline(xintercept = 0, colour = baseline_col, linewidth = 0.4) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high), colour = pal_blue, linewidth = 0.7, size = 0.5) +
  facet_wrap(~outcome, scales = "free_x") +
  labs(x = "Estimated change in score vs reference (95% CI)", y = NULL,
       title = "Predictors of P3CEQ scores",
       subtitle = "Reference categories: English only, Female, Under 45; number of conditions is a linear term (per additional condition)") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0))
```

## What patients said {#sec-comment_racgp_q}

Questions 1, 2 and 3 invited respondents to comment on reception, privacy and coordination.

```{r}
#| label: rate7-comments

comment_table <- function(var, heading) {
  txt <- survey[[var]][!is.na(survey[[var]]) & str_trim(survey[[var]]) != ""]
  if (length(txt) == 0) return(invisible(NULL))
  # A respondent's free text can itself contain a line break (or blank line); left as-is that
  # reads to pandoc as ending the list item, so the rest of the comment spills out as its own
  # paragraph or a separate bullet. Squish each comment onto one line first so it stays one item.
  txt <- str_squish(txt)
  cat("\n**", heading, "** (", length(txt), " comments)\n\n", sep = "")
  cat(paste0("- ", txt, collapse = "\n"), "\n")
}
```

::: {.callout-note collapse="true"}
### Free-text comments on reception, privacy and coordination

```{r}
#| label: rate7-comments-out
#| results: asis

comment_table("q1_comment", "Reception staff")
comment_table("q2_comment", "Privacy")
comment_table("q3_comment", "Coordination with other healthcare professionals")
```
:::

Question 21 asked what one thing respondents would change about the practice.

::: {.callout-note collapse="true"}
### Free-text: "If you could change one thing about the practice..." (Q21)

```{r}
#| label: q21-comments
#| results: asis

comment_table("q21", "Suggested changes")
```
:::

::: {.content-visible when-format="html"}
<script>
// Appends a "View source on GitHub" link below the table of contents in the
// HTML sidebar. Injected via JS (rather than placed in the document body)
// because the sidebar TOC is generated separately by the Quarto/pandoc
// template - markdown content here would render in the main article column,
// not the sidebar.
document.addEventListener("DOMContentLoaded", function () {
  var sidebar = document.querySelector("#quarto-margin-sidebar");
  if (!sidebar) return;
  var div = document.createElement("div");
  div.className = "toc-source-link";
  div.style.marginTop = "1em";
  div.innerHTML =
    '<a href="https://github.com/DavidPatShuiFong/KensingtonPatientSurvey2026/" target="_blank" rel="noopener" style="display:inline-flex;align-items:center;gap:0.4em;font-size:0.9em;">' +
    '<svg height="16" viewBox="0 0 16 16" width="16" aria-hidden="true" style="fill:currentColor;"><path d="M8 0c4.42 0 8 3.58 8 8a8.013 8.013 0 0 1-5.45 7.59c-.4.08-.55-.17-.55-.38 0-.27.01-1.13.01-2.2 0-.75-.25-1.23-.54-1.48 1.78-.2 3.65-.88 3.65-3.95 0-.88-.31-1.59-.82-2.15.08-.2.36-1.02-.08-2.12 0 0-.67-.22-2.2.82-.64-.18-1.32-.27-2-.27-.68 0-1.36.09-2 .27-1.53-1.03-2.2-.82-2.2-.82-.44 1.1-.16 1.92-.08 2.12-.51.56-.82 1.28-.82 2.15 0 3.06 1.86 3.75 3.64 3.95-.23.2-.44.55-.51 1.07-.46.21-1.61.55-2.33-.66-.15-.24-.6-.83-1.23-.82-.67.01-.27.38.01.53.34.19.73.9.82 1.13.16.45.68 1.31 2.69.94 0 .67.01 1.3.01 1.49 0 .21-.15.45-.55.38A7.995 7.995 0 0 1 0 8c0-4.42 3.58-8 8-8Z"></path></svg>' +
    "View source on GitHub</a>";
  sidebar.appendChild(div);
});
</script>
:::

::: {.content-visible when-format="pdf"}
**Source code:** <https://github.com/DavidPatShuiFong/KensingtonPatientSurvey2026/>
:::

## Notes

### Age-sex standardisation {#sec-standardisation}

The Australia and OECD PaRIS figures in [Confidence to self-manage and person-centred care vs
PaRIS10 Dashboard 2024](#confidence-to-self-manage-and-person-centred-care-vs-paris10-dashboard-2024)
are age-sex standardised: each country's raw estimate is reweighted to the *PaRIS standard
population* — a reference age (four bands: 45–54, 55–64, 65–74, 75+) and sex (male/female)
distribution for PaRIS-eligible patients aged 45+, built from the 17 participating OECD member
countries' own standard populations [@oecd-paris, Table 7.5] — via a multilevel regression with
re-centred age/sex predictors [@groenewegen2024], rather than each country's raw sample
composition.

To keep Kensington comparable, its figures in that section are age-sex standardised the same way:
respondents are split into the four age × sex strata that `q26` (45–64 / 65+) and `q22`
(male/female) support, and each stratum's estimate is reweighted to the OECD standard population's
age (collapsed to Kensington's two age bands: 53% 45–64, 47% 65+) and sex (55% female, 45% male)
shares, assumed independent of one another since the OECD report publishes only these two marginal
distributions, not their cross-tabulation. This direct stratum-reweighting is the saturated
(fully-interacted) special case of Groenewegen et al.'s re-centred-regression standardisation
method [-@groenewegen2024] — appropriate here since Kensington is a single site with no
practice/country clustering to model.

## Appendices {#sec-appendices}

::: {.callout-note collapse="true"}
### P3CEQ PC and CC subscale scores by number of long-term conditions: sample sizes

```{r}
#| label: tbl-p3ceq-subscales-by-conditions
#| tbl-cap: "P3CEQ PC and CC subscale scores by number of long-term conditions: underlying means and sample sizes"

subscale_summary |>
  arrange(subscale, condition_band) |>
  transmute(
    `Number of conditions` = condition_band,
    Subscale = subscale,
    `Mean score` = round(mean_score, 1),
    n
  ) |>
  kable(align = "llrr")
```
:::

::: {.callout-note collapse="true"}
### RACGP care continuity and coordination item by number of long-term conditions: sample sizes
```{r}
#| label: tbl-rate7-q3-by-conditions
#| tbl-cap: "Q3 RACGP care continuity and coordination items by number of long-term conditions: underlying means and sample sizes"

q3_summary |>
  arrange(item, condition_band) |>
  transmute(
    `Number of conditions` = condition_band,
    Item = item,
    `Mean rating` = number(mean_rating, accuracy = 0.1),
    n
  ) |>
  kable(align = "llrr")
```
:::

::: {.callout-note collapse="true"}
### P3CEQ PC and CC subscale scores by language: sample sizes
```{r}
#| label: tbl-p3ceq-subscales-by-language
#| tbl-cap: "P3CEQ PC and CC subscale scores by language spoken at home, respondents with 1+ long-term conditions: underlying means and sample sizes"

language_summary |>
  arrange(subscale, language_group) |>
  transmute(
    `Language spoken at home` = language_group,
    Subscale = subscale,
    `Mean score` = round(mean_score, 1),
    n
  ) |>
  kable(align = "llrr")
```
:::

::: {.callout-note collapse="true"}
### Predictors of P3CEQ scores: full regression output

```{r}
#| label: tbl-p3ceq-regression
#| tbl-cap: "Predictors of P3CEQ scores: full coefficient table (language, gender, age)"

reg_coefs |>
  arrange(outcome, term) |>
  transmute(
    Outcome = outcome,
    Term = term,
    n,
    Estimate = number(estimate, accuracy = 0.01),
    `95% CI` = paste0(number(conf.low, accuracy = 0.01), " to ", number(conf.high, accuracy = 0.01)),
    `p` = number(p.value, accuracy = 0.001)
  ) |>
  kable(align = "llrrrr")
```

```{r}
#| label: tbl-p3ceq-regression-fit
#| tbl-cap: "Predictors of P3CEQ scores: model fit statistics"

map_dfr(names(reg_models), function(nm) {
  broom::glance(reg_models[[nm]]) |>
    transmute(
      Outcome = reg_outcome_labels[[nm]],
      n = nobs(reg_models[[nm]]),
      `R²` = number(r.squared, accuracy = 0.01),
      `Adj. R²` = number(adj.r.squared, accuracy = 0.01),
      `F p-value` = number(p.value, accuracy = 0.001)
    )
}) |>
  kable(align = "lrrrr")
```
:::

## References {-}

::: {#refs}
:::
