---
title: "cohealth Kensington GP Clinic — Patient Feedback Survey 2026"
subtitle: "P3CEQ person-centred care results and patient experience summary"
date: today
format:
  html:
    toc: true
    toc-depth: 2
    code-fold: true
    code-summary: "Show the code"
    embed-resources: true
    theme: flatly
  pdf:
    toc: true
    toc-depth: 2
    number-sections: false
    fig-pos: "H"
    geometry:
      - margin=2.5cm
    echo: false
execute:
  warning: false
  message: false
references:
  - type: webpage
    id: paris
    author:
      - literal: "Australian Commission on Safety and Quality in Health Care"
    title: "PaRIS Survey - Australian National Report 2025"
    url: "https://www.safetyandquality.gov.au/resources/paris-survey-australian-national-report-2025"
    issued:
      date-parts:
        - [2025]
    accessed:
      date-parts:
        - [2026, 9, 12]
  - type: webpage
    id: racgppatientfeedbackguide
    author:
      - literal: "RACGP"
    title: "Standards for general practices (5th edition), Patient feedback guide"
    url: "https://www.racgp.org.au/running-a-practice/practice-standards/standards-5th-edition/patient-feedback-guide"
    issued:
      date-parts:
        - [2023, 8]
    accessed:
      date-parts:
        - [2026, 9, 12]
  - type: webpage
    id: p3c_p3c-eq
    author:
      - literal: "University of Plymouth"
    title: "Person centred coordinated experience questionnaire P3C-EQ"
    url: "http://p3c.org.uk/prom-detail/29#ChildVerticalTab_11"
    issued:
      date-parts:
        - [2017]
    accessed:
      date-parts:
        - [2026, 9, 12]
editor: source
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(readxl)
library(scales)
library(knitr)

# Figures are sized (fig-width/fig-height) per chunk for comfortable HTML
# layout; out.width scales the embedded image to fit the page/column in both
# HTML and PDF output so nothing overflows a PDF page's margins. cairo_pdf
# (instead of the base "pdf" device) renders Unicode characters (en dashes,
# em dashes) correctly when the format is PDF.
opts_chunk$set(out.width = "100%")
if (knitr::is_latex_output()) opts_chunk$set(dev = "cairo_pdf")

csv_path  <- "Patient feedback questionnaire — cohealth Kensington GP clinic 2026_WIDE.csv"
form_path <- "kensington_p3ceq_2026_surveycto.xlsx"

# ---- palette (dataviz skill default palette) ---------------------------
pal_blue   <- "#2a78d6"
pal_seq    <- c("#9ec5f4", "#6da7ec", "#3987e5", "#2a78d6", "#1c5cab") # light -> dark, 5 steps
pal_cat    <- c("#2a78d6", "#eb6834", "#1baf7a", "#eda100",
                 "#e87ba4", "#008300", "#4a3aa7", "#e34948")
ink_primary   <- "#0b0b0b"
ink_secondary <- "#52514e"
ink_muted     <- "#898781"
grid_col      <- "#e1e0d9"
baseline_col  <- "#c3c2b7"

theme_report <- theme_minimal(base_size = 12) +
  theme(
    text = element_text(colour = ink_primary),
    plot.title = element_text(face = "bold", size = 13, colour = ink_primary),
    plot.subtitle = element_text(colour = ink_secondary, size = 10.5),
    axis.text = element_text(colour = ink_secondary),
    axis.title = element_text(colour = ink_secondary, size = 10),
    panel.grid.major.x = element_line(colour = grid_col, linewidth = 0.3),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line.y = element_line(colour = baseline_col, linewidth = 0.4),
    axis.ticks = element_blank(),
    legend.title = element_blank(),
    legend.position = "top",
    legend.justification = "left",
    plot.title.position = "plot"
  )
theme_set(theme_report)

strip_html <- function(x) x |> str_remove_all("<[^>]+>") |> str_squish()
```

## About this report

This report summarises responses to the 2026 cohealth Kensington GP clinic patient feedback
survey. The survey combines clinic-specific items about reception, privacy and
care coordination and demographic questions from "Standards for general practices (5th edition), Patient feedback guide" [@racgppatientfeedbackguide]
and the validated **P3CEQ** (Person Centred Coordinated Care Experiences Questionnaire) [@p3c_p3c-eq].

Full item wording and response options are
defined in `` `r form_path` ``; the P3CEQ instrument and its official scoring rules are documented in
`P3C-PEQ with scoring.pdf`.

```{r}
#| label: load-data

raw <- read_csv(csv_path, show_col_types = FALSE, name_repair = "minimal")

# Entries copied in from a paper survey are marked in q1_comment with "PAPER" optionally
# followed by a number (e.g. "PAPER1", "PAPER 12"). Flag those rows, then strip the marker
# out of q1_comment so it doesn't show up as if it were part of the patient's comment.
paper_marker <- regex("PAPER\\s*\\d*")
raw <- raw |>
  mutate(
    # coalesce so a blank q1_comment (str_detect would return NA) reads as "not paper", not NA
    is_paper = coalesce(str_detect(q1_comment, paper_marker), FALSE),
    q1_comment = str_remove(q1_comment, paper_marker) |> str_squish() |> na_if("")
  )

form_survey  <- read_excel(form_path, sheet = "survey")  |> select(type, name, label)
form_choices <- read_excel(form_path, sheet = "choices") |> mutate(value = as.character(value))

# return a labelled vector of choice responses
choice_labels <- function(list_name) {
  form_choices |>
    filter(list_name == !!list_name) |>
    select(value, label) |>
    deframe() # change dataframe to vector
}

# return 'labels' of a question (often the question itself)
item_label <- function(varname) {
  lab <- form_survey$label[form_survey$name == varname]
  if (length(lab) == 0 || is.na(lab)) return(varname)
  strip_html(lab)
}

survey <- raw |> filter(consent == 1)
```

### Participation

```{r}
#| label: participation

n_total     <- nrow(raw)
n_consented <- nrow(survey)
n_declined  <- n_total - n_consented

n_paper  <- sum(survey$is_paper)
n_online <- n_consented - n_paper

# Collection period and completion time are only meaningful for the online arm: a paper
# form's SubmissionDate/duration record when staff later transcribed it, not when the
# patient actually filled it in (paper collection dates are given in the prose below instead).
dates <- raw |>
  filter(!is_paper) |>
  mutate(submit_dt = lubridate::mdy_hms(SubmissionDate)) |>
  summarise(first = min(submit_dt, na.rm = TRUE), last = max(submit_dt, na.rm = TRUE))

med_duration <- median(survey$duration[!survey$is_paper], na.rm = TRUE) / 60

tibble(
  Measure = c("Total submissions", "Consented (analysed below)", "— Online", "— Paper",
              "Declined consent (online)", "Collection period (online)",
              "Median completion time (online)"),
  Value = c(
    n_total,
    n_consented,
    n_online,
    n_paper,
    n_declined,
    paste(format(dates$first, "%d %b %Y"), "–", format(dates$last, "%d %b %Y")),
    paste0(round(med_duration, 1), " minutes")
  )
) |>
  kable(align = "l")
```

Both paper and online versions of the survey were made available. The paper and online versions of the survey were
identical and available in English only.

Paper versions of the survey were offered to patients in the waiting and consulting rooms (11th August to 11th September 2026).

RACGP active patients (three visits or more in the past two years with GP clinicians
at the cohealth Kensington site) who also had seen a cohealth Kensington GP at least once in 2026 and aged 20 years or above
were sent a SMS invitation to complete the survey online on 5th September 2026. 948 patients were invited to complete the survey
through an SMS invitation.

The summaries below are based on those `r n_consented` responses. `r n_declined` people opened the survey online and
declined.

## P3CEQ: person-centred coordinated care experience

Questions 4–20 of the survey reproduce the P3CEQ instrument, using wording as adapted by
the PaRIS international patient reported indicator survey [ACSQHC, -@paris]. Raw response codes are recoded onto the official P3CEQ 0–3 scale before
scoring, following the mapping in `CLAUDE.md`. The total score sums the ten P3CEQ items
(Q7 contributes the average of its four sub-items 7a–7d), giving a score out of 30 where higher
means a more person-centred, coordinated care experience. Two optional subscales are also
reported: **person-centred (PC)** and **care coordination (CC)**.

```{r}
#| label: p3ceq-recode

recode_yesdef  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)
# q7 ("Were there times when you had to repeat information...") is a negatively-framed yesdef
# item, unlike q4/q5/q6/q8: "Yes, definitely" here means the bad thing happened a lot, not that
# a good thing happened. The original P3CEQ Q4 is reverse-scored for exactly this reason (Not at
# all=3 ... Always=0), so the recode must flip polarity vs. recode_yesdef to keep "higher = better"
# consistent across all ten items.
recode_yesdef_reverse <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q10     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 3, x == 4 ~ 0, TRUE ~ NA_real_)
recode_yesno3  <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 0, TRUE ~ NA_real_)
recode_extent5 <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 0, TRUE ~ NA_real_)
recode_q17     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 0, x == 3 ~ 1, x == 4 ~ 2, x == 5 ~ 3, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q18     <- function(x) case_when(x == 1 ~ 0, x == 2 ~ 1, x == 3 ~ 2, x == 4 ~ 3, x == 5 ~ 2, x == 6 ~ 0, x == 7 ~ 0, TRUE ~ NA_real_)
recode_q19     <- function(x) case_when(x == 1 ~ 3, x == 2 ~ 2, x == 3 ~ 1, x == 4 ~ 0, x == 5 ~ 0, TRUE ~ NA_real_)

p3ceq <- survey |>
  transmute(
    KEY,
    p1  = recode_yesdef(q4),
    p2  = recode_yesdef(q5),
    p3  = recode_yesdef(q6),
    p4  = recode_yesdef_reverse(q7),
    p5  = recode_yesdef(q8),
    p6  = recode_q10(q10),
    p7a = recode_yesno3(q13),
    p7b = recode_yesno3(q14),
    p7c = recode_extent5(q15),
    p7d = recode_extent5(q16),
    p8  = recode_q17(q17),
    p9  = recode_q18(q18),
    p10 = recode_q19(q19)
  ) |>
  mutate(
    p7 = if_else(p7a == 0, 0, rowMeans(cbind(p7a, p7b, p7c, p7d), na.rm = FALSE))
  ) |>
  mutate(
    total       = p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10,
    pc_subscale = p1 + p2 + p3 + p4 + p5 + p8 + p9 + p10,
    cc_subscale = p5 + p6 + p7 + p8 + p9
  )
```

### Total and subscale scores

```{r}
#| label: p3ceq-scores

score_summary <- function(x, label, max_score) {
  tibble(
    Score = label,
    n = sum(!is.na(x)),
    Mean = mean(x, na.rm = TRUE),
    Median = median(x, na.rm = TRUE),
    SD = sd(x, na.rm = TRUE),
    `Out of` = max_score
  )
}

bind_rows(
  score_summary(p3ceq$total, "P3CEQ total", 30),
  score_summary(p3ceq$pc_subscale, "Person-centred subscale (PC)", 24),
  score_summary(p3ceq$cc_subscale, "Care coordination subscale (CC)", 15)
) |>
  mutate(across(c(Mean, Median, SD), \(x) round(x, 1))) |>
  kable(align = "lrrrrr")
```

```{r}
#| label: fig-p3ceq-total-dist
#| fig-cap: "Distribution of P3CEQ total scores (0–30, higher = more person-centred)"

p3ceq |>
  filter(!is.na(total)) |>
  ggplot(aes(total)) +
  geom_histogram(binwidth = 2, boundary = 0, fill = pal_blue, colour = "white", linewidth = 0.3) +
  scale_x_continuous(limits = c(0, 30), breaks = seq(0, 30, 5)) +
  labs(x = "P3CEQ total score", y = "Respondents", title = "P3CEQ total score distribution")
```

### Care coordination subscale vs PaRIS 2023

cohealth Kensington general practice previously conducted the P3CEQ survey in 2023 as part of PaRIS [@paris].
As pat of PaRIS, 193 patients aged 45+ years of the cohealth Kensington clinic returned a survey.

PaRIS reported the P3CEQ care coordination (CC) subscale breakdown, comparing Kensington's own patients
against a national comparison group (see `P3CEQ coordinated care subscale PaRIS 2023.png`).

```{r}
cc_bands <- c("Very low (0–3)", "Low (3.01–6)", "Moderate (6.01–9)", "High (9.01–12)", "Very high (12.01–15)")

# Reference percentages read off "P3CEQ coordinated care subscale PaRIS 2023.png" - no digital
# source for these exists, only that chart image (Kensington's 2023 PaRIS results and the PaRIS
# national comparison group). Average scores from the same image: 8.8 (Kensington 2023, Moderate)
# and 9.8 (PaRIS comparison 2023).
cc_paris_2023 <- tibble(
  band = factor(cc_bands, levels = cc_bands),
  `Kensington 2023`        = c(10, 19, 24, 23, 24),
  `PaRIS comparison 2023`  = c(6, 14, 24, 33, 23)
)

band_of_cc <- function(x) cut(x, breaks = c(0, 3, 6, 9, 12, 15), labels = cc_bands, include.lowest = TRUE)

cc_2026_data <- p3ceq |>
  left_join(survey |> select(KEY, q26), by = "KEY") |>
  filter(q26 %in% c(3, 4), !is.na(cc_subscale)) # age 45-64 (3) or 65+ (4), per q26opts

cc_2026_bands <- cc_2026_data |>
  mutate(band = band_of_cc(cc_subscale)) |>
  count(band, .drop = FALSE) |>
  mutate(`Kensington 2026` = n / sum(n) * 100) |>
  select(band, `Kensington 2026`)

cc_compare <- cc_paris_2023 |>
  left_join(cc_2026_bands, by = "band") |>
  pivot_longer(-band, names_to = "series", values_to = "pct") |>
  mutate(series = factor(series, levels = c("Kensington 2023", "PaRIS comparison 2023", "Kensington 2026")))
```

```{r}
#| label: cc-subscale-avg

avg_cc_2026 <- mean(cc_2026_data$cc_subscale)
n_cc_2026   <- nrow(cc_2026_data)
```

Average P3CEQ care coordination subscale score among respondents aged 45+ (n = `r n_cc_2026`) was
**`r round(avg_cc_2026, 1)` ** (`r band_of_cc(avg_cc_2026)`) for Kensington 2026.
This compares to 8.8 (Moderate) for Kensington 2023 and 9.8 for the PaRIS 2023 comparison group.

```{r}
#| label: fig-cc-subscale-paris
#| fig-cap: "P3CEQ care coordination subscale (0–15), patients aged 45+: Kensington 2026 vs PaRIS 2023"
#| fig-width: 8
#| fig-height: 4.5

ggplot(cc_compare, aes(pct, fct_rev(band), fill = series)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  geom_text(aes(label = paste0(round(pct), "%")), position = position_dodge(width = 0.75),
            hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_fill_manual(values = pal_cat[1:3]) +
  scale_x_continuous(limits = c(0, max(cc_compare$pct, na.rm = TRUE) * 1.15)) +
  labs(x = "Share of respondents aged 45+", y = NULL)
```

### Item-level results

```{r}
#| label: fig-p3ceq-items
#| fig-cap: "Mean score per P3CEQ item (0–3 scale, higher = better)"
#| fig-height: 5

p3ceq_item_labels <- c(
  p1  = "Q1. Discussed what matters to you",
  p2  = "Q2. Involved in decisions about your care",
  p3  = "Q3. Considered as a whole person",
  p4  = "Q4. Didn't have to repeat information*",
  p5  = "Q5. Healthcare joined up / works for you",
  p6  = "Q6. Has a single coordinating professional",
  p7  = "Q7. Care plan in place and followed (avg of 7a–7d)",
  p8  = "Q8. Enough support to manage own health",
  p9  = "Q9. Useful information when needed",
  p10 = "Q10. Confident managing own health"
)

p3ceq |>
  select(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10) |>
  pivot_longer(everything(), names_to = "item", values_to = "score") |>
  filter(!is.na(score)) |>
  group_by(item) |>
  summarise(mean_score = mean(score), n = n(), .groups = "drop") |>
  mutate(item = fct_reorder(p3ceq_item_labels[item], mean_score)) |>
  ggplot(aes(mean_score, item)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = number(mean_score, accuracy = 0.1)),
            hjust = -0.3, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, 3.4), breaks = 0:3) +
  labs(x = "Mean score (0–3)", y = NULL,
       title = "P3CEQ item scores",
       subtitle = "*Q4 is reverse-scored: a high score means information rarely had to be repeated")
```

## Clinic-specific experience

Questions 1–3 ask about reception staff, privacy, and how well your clinician coordinated with
other health professionals, each rated on a 5-point Poor–Excellent scale (with "N/A" and "Don't
know" excluded from the summaries below).

```{r}
#| label: fig-rate7-items
#| fig-cap: "Reception, privacy and clinician coordination — response distribution (valid responses only)"
#| fig-width: 9
#| fig-height: 5.5

rate7_labs <- choice_labels("rate7")
rate7_valid <- names(rate7_labs)[!rate7_labs %in% c("N/A", "Don't know")]

rate7_vars <- c("q1a", "q1b", "q1c", "q2a", "q2b", "q2c", "q3a", "q3b", "q3c", "q3d")

rate7_long <- survey |>
  select(all_of(rate7_vars)) |>
  mutate(across(everything(), as.character)) |>
  pivot_longer(everything(), names_to = "var", values_to = "value") |>
  filter(value %in% rate7_valid) |>
  mutate(
    item = fct_rev(fct_inorder(map_chr(var, item_label))),
    response = factor(rate7_labs[value], levels = rate7_labs[rate7_valid])
  )

rate7_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(pct, item, fill = response)) +
  geom_col(width = 0.7, position = position_stack(reverse = TRUE)) +
  scale_fill_manual(values = pal_seq) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
  labs(x = "Share of valid responses", y = NULL, title = "Ratings by item") +
  theme(legend.position = "top")
```

```{r}
#| label: rate7-comments

comment_table <- function(var, heading) {
  txt <- survey[[var]][!is.na(survey[[var]]) & str_trim(survey[[var]]) != ""]
  if (length(txt) == 0) return(invisible(NULL))
  cat("\n**", heading, "** (", length(txt), " comments)\n\n", sep = "")
  cat(paste0("- ", txt, collapse = "\n"), "\n")
}
```

::: {.callout-note collapse="true"}
## Free-text comments on reception, privacy and coordination

```{r}
#| label: rate7-comments-out
#| results: asis

comment_table("q1_comment", "Reception staff")
comment_table("q2_comment", "Privacy")
comment_table("q3_comment", "Coordination with other healthcare professionals")
```
:::

## Long-term conditions

```{r}
#| label: fig-conditions
#| fig-cap: "Long-term conditions reported by respondents"
#| fig-width: 8
#| fig-height: 7

summarise_multiselect <- function(data, prefix, list_name) {
  labs <- choice_labels(list_name)
  cols <- data |> select(matches(paste0("^", prefix, "_[0-9]+$")))
  tibble(
    value = str_remove(names(cols), paste0("^", prefix, "_")),
    n = colSums(cols, na.rm = TRUE)
  ) |>
    mutate(label = labs[value], pct = n / nrow(data)) |>
    arrange(desc(n))
}

conditions <- summarise_multiselect(survey, "q9", "conditions")

conditions |>
  mutate(label = fct_reorder(str_wrap(label, 28), n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(conditions$n) * 1.15)) +
  labs(x = "Respondents", y = NULL, title = "Long-term conditions (Q9)",
       subtitle = paste0("Out of ", n_consented, " respondents; multiple selections allowed"))
```

Q9 also lets respondents specify "Other long-term condition(s)" as free text. `q9_other` holds
what respondents typed in; below are those responses as given, one row per respondent.

```{r}
#| label: tbl-conditions-other
#| tbl-cap: "Q9 \"Other long-term condition(s)\": free-text responses"

other_conditions <- survey |>
  mutate(q9_other = str_squish(q9_other)) |>
  filter(!is.na(q9_other), q9_other != "") |>
  transmute(`Free-text response` = q9_other)

kable(other_conditions, align = "l")
```

`r nrow(other_conditions)` free-text responses, out of `r conditions$n[conditions$label == "Other long-term condition(s) (please specify)"]`
respondents who selected "Other long-term condition(s)".

## Respondent profile

```{r}
#| label: fig-demographics
#| fig-cap: "Respondent demographics"
#| fig-width: 11
#| fig-height: 12

demo_vars <- tribble(
  ~var, ~list, ~title,
  "q22", "q22opts", "Gender (Q22)",
  "q26", "q26opts", "Age (Q26)",
  "q27", "q27opts", "Time at this practice (Q27)",
  "q29", "q29opts", "Visits in past 12 months (Q29)",
  "q30", "q30opts", "Highest education level (Q30)",
  "q31", "q31opts", "Visit was for self or someone else (Q31)",
  "q23", "yesno",   "Aboriginal/Torres Strait Islander (Q23)",
  "q24", "yesno",   "Attended another GP practice in past year (Q24)"
)

demo_long <- pmap_dfr(demo_vars, function(var, list, title) {
  labs <- choice_labels(list)
  survey |>
    mutate(value = as.character(.data[[var]])) |>
    filter(!is.na(value), value %in% names(labs)) |>
    count(value) |>
    mutate(
      question = title,
      response = factor(labs[value], levels = labs),
      pct = n / sum(n)
    )
})

demo_long |>
  ggplot(aes(pct, fct_rev(response))) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = percent(pct, accuracy = 1)), hjust = -0.2, size = 3, colour = ink_secondary) +
  scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.25))) +
  facet_wrap(~question, scales = "free_y", ncol = 2) +
  labs(x = NULL, y = NULL, title = "Who responded") +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

```{r}
#| label: demographics-extra

languages <- summarise_multiselect(survey, "q25", "languages")
concession <- summarise_multiselect(survey, "q28", "q28opts")
```

```{r}
#| label: fig-languages
#| fig-cap: "Languages spoken at home (Q25) and concession cards held (Q28)"
#| fig-width: 10
#| fig-height: 4.5

bind_rows(
  languages |> mutate(facet = "Languages spoken at home (Q25)"),
  concession |> mutate(facet = "Concession cards held (Q28)")
) |>
  mutate(label = fct_reorder(label, n)) |>
  ggplot(aes(n, label)) +
  geom_col(fill = pal_blue, width = 0.7) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.2, colour = ink_secondary) +
  facet_wrap(~facet, scales = "free", ncol = 2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(x = "Respondents", y = NULL) +
  theme(strip.text = element_text(face = "bold", colour = ink_primary, hjust = 0),
        panel.spacing.x = unit(1.4, "lines"))
```

A large share of the Q25 "Other" responses come from a wide mix of languages, none individually
common enough to be listed as its own choice on the form. `q25_other` holds what respondents
typed in; below are those free-text responses as given (grouped only where the text matches
exactly), most-common first.

```{r}
#| label: fig-languages-other
#| fig-cap: "Q25 'Other' responses: languages named in free text"
#| fig-width: 7
#| fig-height: 4

other_langs <- survey |>
  mutate(q25_other = str_squish(q25_other)) |>
  filter(!is.na(q25_other), q25_other != "") |>
  count(q25_other, sort = TRUE)

other_langs |>
  mutate(q25_other = fct_reorder(q25_other, n)) |>
  ggplot(aes(n, q25_other)) +
  geom_col(fill = pal_blue, width = 0.6) +
  geom_text(aes(label = n), hjust = -0.4, size = 3.3, colour = ink_secondary) +
  scale_x_continuous(limits = c(0, max(other_langs$n) * 1.15), breaks = scales::breaks_pretty()) +
  labs(x = "Respondents", y = NULL, title = "Q25 \"Other\": languages named in free text",
       subtitle = paste0(sum(other_langs$n), " free-text responses, out of ",
                          languages$n[languages$label == "Other"], " respondents who selected \"Other\""))
```

## What patients said

Question 21 asked what one thing respondents would change about the practice.

::: {.callout-note collapse="true"}
## Free-text: "If you could change one thing about the practice..." (Q21)

```{r}
#| label: q21-comments
#| results: asis

comment_table("q21", "Suggested changes")
```
:::
